Regular singular Volterra equations on complex domains

### 2025-01-28 sima/correspondence/sima-cover.tex
Revert accidental changes to cover letter
This reverts commit 8eb7acca3edcc637157af873d4393e0cd7a6185f.

\address{Campbell Wheeler \\
Institut des Hautes \'{E}tudes Scientifiques \\
Le Bois-Marie, 35 route de Chartres \\
F-91440 Bures-sur-Yvette, France}

\signature{\vspace{-12mm}Campbell Wheeler \\
\url{wheeler@ihes.fr} \\[6pt]
Veronica Fantini \\
\url{veronica.fantini@universite-paris-saclay.fr}}

@@

\date{January 10, 2025}

>>>>

\address{Veronica Fantini \\
Institut des Hautes \'{E}tudes Scientifiques \\
Le Bois-Marie, 35 route de Chartres \\
F-91440 Bures-sur-Yvette, France}

\signature{\vspace{-12mm}Veronica Fantini \\
\url{fantini@ihes.fr} \\[6pt]
Aaron Fenyes \\
\url{aaron.fenyes@fareycircles.ooo}}

@@

\date{Octobter 31, 2023}
